---
title       : Kaggle dojo
subtitle    : 
author      : 
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Kaggle

* Kaggle hosts data driven insights competitions online
* Popular in the machine learning community
* Recently they started hosting interesting data sets such as...


--- 

## Hillary Clinton's emails!

* Background: Hillary Clinton was using personal email during her time as Secretary of state. 
* Caused controversy due it possibly violating transperancy protocols.
* 7000+ pdfs parsed and cleaned by kaggle

```{r clinton, echo = FALSE, message = FALSE, warning = FALSE}
source("../shitClintonSays.R")

emails <- data.table(read.csv("~/Downloads/output/Emails.csv"))
persons <- data.table(read.csv("~/Downloads/output/Persons.csv"))
emails.with.person <- merge(emails, persons[, list(SenderPersonId = Id)], by = "SenderPersonId", all.x = TRUE)

emails.to.hill <- emails[MetadataTo == "H"]
emails.from.hill <- emails[MetadataFrom == "H"]

freq.to.h = wordFrequencyFor(emails.to.hill)
freq.from.h = wordFrequencyFor(emails.from.hill)
```

---

```{r from, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 14}
par(mfcol=c(1,2))
printWordCloudFor(freq.to.h, min.freq = 150)
printWordCloudFor(freq.from.h, min.freq = 5)
```




